R Markdown for Reproducible Research

### 2019-01-25 paper.Rmd
remove symbol
add clarification about needing R installed

If Markdown is a lightweight markup language and text formatting syntax, R
Markdown must be Markdown + R code, right? Yes, with a catch. R Markdown
actually supports _many_ programming languages and output types. It got its
start with R, and R is the primary language engine, but R is an interface
language. This means that R has been (from its outset) commonly used to "wrap"
or call other programming languages. This began as Fortran and C, but has
expanded to include C++, Python, JavaScript, SQL, Stan, and more. As a result, R
Markdown supports the inclusion of many of these programming languages.

@@

There is [much
more](https://bookdown.org/yihui/rmarkdown/parameterized-reports.html) available
to explore in Parameterized R Markdown, like an easy-to-use [user
interface](https://bookdown.org/yihui/rmarkdown/params-knit.html#the-interactive-user-interface)
for selecting values. You can also host Parameterized R Markdown in a publishing
platform like RStudio Connect that [exposes a user interface to end
users](https://docs.rstudio.com/connect/user/param-rmarkdown.html#publish-param-rmarkdown)
of a report.

>>>>

If Markdown is a lightweight markup language and text formatting syntax, R
Markdown must be Markdown plus R code, right? Yes, with a catch. R Markdown
actually supports _many_ programming languages and output types. It got its
start with R, and R is the primary language engine, but R is an interface
language. This means that R has been (from its outset) commonly used to "wrap"
or call other programming languages. This began as Fortran and C, but has
expanded to include C++, Python, JavaScript, SQL, Stan, and more. As a result, R
Markdown supports the inclusion of many of these programming languages.

@@

There is [much
more](https://bookdown.org/yihui/rmarkdown/parameterized-reports.html) available
to explore in Parameterized R Markdown, like an easy-to-use [user
interface](https://bookdown.org/yihui/rmarkdown/params-knit.html#the-interactive-user-interface)
for selecting values. You can also host Parameterized R Markdown in a publishing
platform like RStudio Connect that [exposes a user interface to end
users](https://docs.rstudio.com/connect/user/param-rmarkdown.html#publish-param-rmarkdown)
of a report without needing them to install R.
